Classless Java

### 2015-11-11 paper/sections/RelatedWork.tex
added references

\subsection{Multiple Inheritance in Object oriented languages}
Many authors have argued in favour or against multiple inheritance.
It provides expressive power, but it is difficult to model, and implement and can create programs that are hard to reason about.
These difficulties include the famous
diamond (fork-join) problem, conflicting methods, and the yo-yo problem.
\marco{add citation on the text over}

To conciliate the need for expressive power and the need for simplicity, 
lots of models have been proposed in the past few
years, including mixins~\cite{bracha90mixin} and traits~\cite{scharli03traits}.
They provide novel programming architecture models in the
OO paradigm. 
\begin{enumerate}
\item  Mixins allows to name components that can be applied to various classes as
reusable functionality units. However,  they suffer from linearisation: the order of mixin application is relevant in often subtitle and undesired ways. constraints. This hinders their
usability and their ability of resolving conflicts:
 the linearisation (total ordering) of mixin inheritance cannot provide a satisfactory resolution in all cases and restricts the flexibility of mixin composition.

>>>>

\subsection{Multiple Inheritance in Object oriented languages}
Many authors have argued in favour or against multiple inheritance.
It provides expressive power, but it is difficult to model, and implement and can create programs that are hard to reason about.
These difficulties include the famous
diamond (fork-join) problem~\cite{bracha90mixin,Sak89dis}, conflicting methods, and the yo-yo problem~\cite{taenzer1989problems}.
\marco{add citation on the text over.}
\yanlin{added.}
To conciliate the need for expressive power and the need for simplicity, 
lots of models have been proposed in the past few
years, including mixins~\cite{bracha90mixin} and traits~\cite{scharli03traits}.
They provide novel programming architecture models in the
OO paradigm. 
\begin{enumerate}
\item  Mixins allows to name components that can be applied to various classes as
reusable functionality units. However,  they suffer from linearisation: the order of mixin application is relevant in often subtitle and undesired ways. constraints. This hinders their
usability and their ability of resolving conflicts:
 the linearisation (total ordering) of mixin inheritance cannot provide a satisfactory resolution in all cases and restricts the flexibility of mixin composition.
